Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-13 paper_comparison/paper_comparison/paper_comparison.Rmd
null simulation

Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualization" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, @buja_statistical_2009 proposed the lineup protocol as a visual test inspired by the "police lineup" or "identity parade" which is the act of asking the eyewitness to identify criminal suspect from a group of irrelevant people. The protocol consists of $m$ randomly placed plots, where one plot is the actual data plot, and the remaining $m - 1$ plots have the identical graphical production as the data plot except the data has been replaced with data consistent with the null hypothesis. Then, an observer who have not seen the actual data plot will be asked to point out the most different plot from the lineup. Figure \ref{fig:first-example-lineup} is an example of a lineup protocol. If the actual data plot at position 11 is identifiable, then it is evidence for the rejection of the null hypothesis that the regression model is correctly specified. In fact, the example lineup is generated from a misspecified regression model with non-linearity issue. So one may notice the cubic curve in the actual residual plot.

Simulation of the null data used in the 19 null plots are

>>>>

Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualization" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, @buja_statistical_2009 proposed the lineup protocol as a visual test inspired by the "police lineup" or "identity parade" which is the act of asking the eyewitness to identify criminal suspect from a group of irrelevant people. The protocol consists of $m$ randomly placed plots, where one plot is the actual data plot, and the remaining $m - 1$ plots have the identical graphical production as the data plot except the data has been replaced with data consistent with the null hypothesis. Then, an observer who have not seen the actual data plot will be asked to point out the most different plot from the lineup. Figure \ref{fig:first-example-lineup} is an example of a lineup protocol. If the actual data plot at position 11 is identifiable, then it is evidence for the rejection of the null hypothesis that the regression model is correctly specified. In fact, the actual residual plot is obtained from a misspecified regression model with non-linearity issue.

Data used in the $m - 1$ null plots needs to be simulated. In the context of regression diagnostics, sampling data from $H_0$ is equivalent to sampling data from the assumed model. As @buja_statistical_2009 suggested, $H_0$ is usually composited by a collection of distributions controlled by nuisance parameters. Since regression models can have various forms, there is no general solution to this problem, but it sometimes can be reduced to so called "reference distribution" by applying one of the three methods: (i) sampling from a conditional distribution given a minimal sufficient statistic under $H_0$, (ii) parametric bootstrap sampling with nuisance parameters estimated under $H_0$, and (iii) Bayesian posterior predictive sampling. The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three [@buja_statistical_2009]. Essentially, null residuals can be simulated by regressing $N$ i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions.

### 2022-09-13 paper_comparison/paper_comparison/paper_comparison.tex
null simulation

Non-normality is usually harder to be detected from a residual plot
compared to non-linearity and heterskedasticity. Besides, a
quantile-quantile plot can often do a better job for this task. Note
that not all regression models assume normality of the error term, but a
certain amount of them does. If this assumption happens to be false,
then it is expected to see data points do not distribute noramlly on the
y-axis. For example, given a skewed error distribution, one will see
fewer data points and more outliers on one side of the zeroline as shown
in the bottom-right of Figure
\textbackslash ref\{fig:commondepartures\}.

@@

Visual inference was first introduced in a 1999 Joint Statistical
Meetings (JSM) talk with the title ``Inference for Data Visualization''
by \citet{buja_inference_1999} as an idea to address the issue of valid
inference for visual discoveries of data plots
\citep{gelman_exploratory_2004}. Later, \citet{buja_statistical_2009}
proposed the lineup protocol as a visual test inspired by the ``police
lineup'' or ``identity parade'' which is the act of asking the
eyewitness to identify criminal suspect from a group of irrelevant
people. The protocol consists of \(m\) randomly placed plots, where one
plot is the actual data plot, and the remaining \(m - 1\) plots have the
identical graphical production as the data plot except the data has been
replaced with data consistent with the null hypothesis. Then, an
observer who have not seen the actual data plot will be asked to point
out the most different plot from the lineup. Figure
\ref{fig:first-example-lineup} is an example of a lineup protocol. If
the actual data plot at position 11 is identifiable, then it is evidence
for the rejection of the null hypothesis that the regression model is
correctly specified. In fact, the example lineup is generated from a
misspecified regression model with non-linearity issue. So one may
notice the cubic curve in the actual residual plot.

Simulation of the null data used in the 19 null plots are

>>>>

Non-normality is usually harder to be detected from a residual plot
compared to non-linearity and heterskedasticity. Besides, a
quantile-quantile plot can often do a better job for this task. Note
that not all regression models assume normality of the error term, but a
certain amount of them does. If this assumption happens to be false,
then it is expected to see data points do not distribute noramlly on the
y-axis. For example, given a skewed error distribution, one will see
fewer data points and more outliers on one side of the zeroline as shown
in the bottom-right of Figure \ref{fig:commondepartures}.

@@

Visual inference was first introduced in a 1999 Joint Statistical
Meetings (JSM) talk with the title ``Inference for Data Visualization''
by \citet{buja_inference_1999} as an idea to address the issue of valid
inference for visual discoveries of data plots
\citep{gelman_exploratory_2004}. Later, \citet{buja_statistical_2009}
proposed the lineup protocol as a visual test inspired by the ``police
lineup'' or ``identity parade'' which is the act of asking the
eyewitness to identify criminal suspect from a group of irrelevant
people. The protocol consists of \(m\) randomly placed plots, where one
plot is the actual data plot, and the remaining \(m - 1\) plots have the
identical graphical production as the data plot except the data has been
replaced with data consistent with the null hypothesis. Then, an
observer who have not seen the actual data plot will be asked to point
out the most different plot from the lineup. Figure
\ref{fig:first-example-lineup} is an example of a lineup protocol. If
the actual data plot at position 11 is identifiable, then it is evidence
for the rejection of the null hypothesis that the regression model is
correctly specified. In fact, the actual residual plot is obtained from
a misspecified regression model with non-linearity issue.

Data used in the \(m - 1\) null plots needs to be simulated. In the
context of regression diagnostics, sampling data from \(H_0\) is
equivalent to sampling data from the assumed model. As
\citet{buja_statistical_2009} suggested, \(H_0\) is usually composited
by a collection of distributions controlled by nuisance parameters.
Since regression models can have various forms, there is no general
solution to this problem, but it sometimes can be reduced to so called
``reference distribution'' by applying one of the three methods: (i)
sampling from a conditional distribution given a minimal sufficient
statistic under \(H_0\), (ii) parametric bootstrap sampling with
nuisance parameters estimated under \(H_0\), and (iii) Bayesian
posterior predictive sampling. The conditional distribution given a
minimal sufficient statistic is the best justified reference
distribution among the three \citep{buja_statistical_2009}. Essentially,
null residuals can be simulated by regressing \(N\) i.i.d standard
normal random draws on the regressors, then rescaling it by the ratio of
residual sum of square in two regressions.
